NIRCam Faint and Bright Flux Calibration Plan

### 2017-05-08 ms.tex
I started removing sections that will only go in the supplement.

\section{Faint White Dwarf Network}
\citet{narayan2016wdnetwork} identified faint (V$\sim$18-19) DA white dwarfs for calibration of surveys such as with LSST, DECam, JWST and PanSTARRS.
These sources are faint enough to avoid saturation with large aperture telescopes and have atmospheres largely characterizable with just two parameters T$_\mathrm{eff}$ and $\log(g)$.
The fact that these DA dwarfs' atmospheres are dominated by hydrogen means that they are relatively simple to model at high resolution for calibrating photometric bandpasses.

Figure \ref{fig:wideFiltWDCalspec} shows NIRCam sensitivity limits (10$\sigma$ in 1 hour), the CALSPEC database and representative G2~V stars identified in this paper which were already displayed in Figure \ref{fig:JWSTcalsWideF}.
Additionally, four stars from \citet{narayan2016wdnetwork} are shown using the WD1657+343 white dwarf model (without extinction) as a placeholder.
These WD stars nicely extend the sample of stars much deeper into the NIRCam sensitivity limit than previous targets.
However, there is the possibility that the models for the stars in \citet{narayan2016wdnetwork} may not work effectively for the near-infrared.
If there are small dust particles surrounding these white dwarfs, they could produce near-IR or mid-IR excesses.
Additionally, there are few measurements into the infrared so extrapolation would be required.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{calspec_and_new_clust_wd.pdf}
\caption{The NIRCam saturation and sensitivities are shown as in Figure \ref{fig:JWSTcalsWideF}.
This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
The faint WD stars extend much farther into the NIRCam sensitivity wells than the CALSPEC and solar analog stars.}\label{fig:wideFiltWDCalspec}
\end{figure}

\clearpage
\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}

@@

\appendix

\section{Notes to Self}

\subsection{Notes on using \texttt{mkclass}}

\subsubsection{Code System}
The library is organized into files like \texttt{t130l50p00.rbn}.
The \texttt{t130} specifies 10 $\times$ the class coding system of O3 through M9 visible in the code \texttt{code3spt.c}.
In this case, \texttt{t130} means code 13.0 and type B7.
The luminosity class is next \texttt{l50} means V.
We use the \texttt{libnor36} library, which appears to work with the "Roughtype 2" method for non-rectified data.
The code runs into segmentation faults if attempting Roughtype 1 with the \texttt{libnor36} library.

\subsubsection{Backgrounds}

Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
From the code documentation: average across the sky has zfact = 2.5.
In these models solar B-V=0.65 for 1~M$_\odot$ at 4.25 Gyr.

\subsection{Isochrones}

As a check on the maximum age, I downloaded Dartmouth Isochrones \citep{dotter2008dartmouth} and plotted the color-magnitude diagram in Figure \ref{fig:isochrones}.
At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188 \citep[7.1 Gyr][]{elsanhoury2016ngc188}.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{hr_isochrones.pdf}
\caption{The Dartmouth isochrones \citep{dotter2008dartmouth}, for [Fe/H]=0, show that the age of the cluster should be $\lesssim 7 $Gyr before main sequence turnoff should begin to affect the identification of solar analogs.
The red vertical line represents solar B-V.}\label{fig:isochrones}
\end{figure}

\subsection{UKIRT Calibration}

Our WFCAM data should be calibrated in a similar was as UKIDSS.
Eiichi Egami says we can use the Viking Survey as an independent check on the UKIDSS flux calibration.

\subsection{Sections to Expand in this Report}

George has some requests for this report.
Consider adding notes on calibration of two more instruments.
The solar spectrum is very well measured at infrared wavelengths, so it may be the best one for interpolation from optical/NIR into Far IR.
\begin{enumerate}
	\item MIRI: For the shorter wavelength MIRI bands (say F560W and F770W) photometry, George would like to observe the NIRCam faint G2V stars in order to have a sample of stars that have a highly accurate solar model
	\item NIRSpec: We'd also want to test calibration of NIRSpec w/ our solar G2 V stars.
George recommends the IFU or slits as opposed to MSA because it's less sensitive to positional accuracy.
Note that we would only get 1 G2V star at a time.
Also, beware that no bright stars from the cluster contaminate the field. MSA shutters that are stuck open may introduce significant amounts of stray light.
\end{enumerate}
Note, that George has two concerns about white dwarfs:
\begin{enumerate}
	\item debris disks emission - they have found that magnetic field trapping of dust around A stars can cause excess emission.
White dwarfs have strong magnetic fields and could also trap nano-grain dust.
George and Andras will probably write a paper on white dwarf dust in Fall of 2017.
	\item uncertainties in the IR - white dwarfs don't have a lot of measurements in the IR.
How can we be sure the models are good in the infrared?
\end{enumerate}
Also, George has one idea with regards to subarray versus full frame imaging.
Maybe we could a bright calibrator star (K$\sim$ 6) on the neutral density filter so that it doesn't saturate full frame.
Then, observe the bright star in subarray and full frame to check the conversion from subarray to full frame for a given filter.
Another idea would be to use a narrow-band filter to check the subarray/full frame conversion.

>>>>

\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}

@@
